---
title: "npmlb: Collecting Baseball Data"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This package is designed to collect baseball data from the web.  Currently the package supports pulling data from the following sites:

https://www.baseball-reference.com/

* Player Game Logs
* HOF Players
* Career Statistics

# Install

To install the latest version use the following code:

```{r, eval = FALSE}
devtools::install_github("nickpaul7/npmlb")
```

# Required Packages

```{r}
library(tidyverse)
```


# Player Game Logs

To get all player game logs for entire season, use the code below.


```{r, eval = FALSE}
npmlb::save_mlb_year(2019)
```


# Get Team Roster

The `scrape_team_full_roster()` function will collect the pitching and batting roster for a given team.

```{r}
team <- "NYY"
year <- "2019"
df_roster <- npmlb::scrape_team_full_roster(team, year)
```

To extract the rosters, you can use the following code.

```{r}
df_roster %>% 
    filter(data_type == "pitching") %>% 
    unnest()
```

The `team_pages` data object contains the abbreviations for each team.

```{r}
npmlb::team_pages
```

# Scrape a Player Page

```{r}
link <- "https://www.baseball-reference.com/players/gl.fcgi?id=lemahdj01&t=b&year=2019"
type = "b"
df_player_log <- npmlb::scrape_player_game_logs(link, type)
```


